Unifying the communicable disease spreading paradigm with Gompertzian growth

### 2022-08-05 ScientificReports/main.tex
use githash for data table

This phenomenon is recorded by others \cite{Ohnishi2020,Rypdal2020,Catala2020,rodrigues2020monte,Levitt2020}, showing Gompertz curves at national levels instead of the traditionally predicted logistic curves. These observations are made possible in part due to the increased cadence and quality of data acquisition compared with earlier epidemics. What is causing such a discrepancy between these observations and the current theory of communicable diseases \cite{castro2020turning}?

@@

>>>>

This phenomenon is recorded by others \cite{Ohnishi2020,Rypdal2020,Catala2020,rodrigues2020monte,Levitt2020}, showing Gompertz curves at national levels instead of the traditionally predicted logistic curves, a conclusion made possible in part due to the increased cadence and quality of data acquisition compared with earlier epidemics. What is causing such a discrepancy between these observations and the current theory of communicable diseases \cite{castro2020turning}?

@@

\subsection*{Data Availability}
Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore,
USA \cite{dong2020interactive}, and are available at \url{https://github.com/CSSEGISandData/COVID-19}, specifically the table \newline\verb|csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv|, \newline downloaded Aug. $5^{th}$ 2022.
